Verifying Demonstrations

### 2018-05-22 paper/LocationProofs.tex
Transforms comments in code to visible comments

To counter this threat, a LBS should ask the requesting device to formally prove that it really is at the claimed location. This notion can be formalized through the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof. 
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
%Seb: to do add the corresponding reference
However, some location proofs systems such as PROPS exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
\PRIVO share some similarities with PROPS although their objective is quite different as we aim at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made a user, which is an individual property.

>>>>

To counter this threat, a LBS should ask the requesting device to formally prove that it really is at the claimed location. This notion can be formalized through the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof. 
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
\seb{to do add the corresponding reference}
However, some location proofs systems such as PROPS exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
\PRIVO share some similarities with PROPS although their objective is quite different as we aim at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made a user, which is an individual property.

### 2018-05-22 paper/intro.tex
Transforms comments in code to visible comments

Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in details in \cref{RelatedWork}).
However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
In addition, they also lack verifiability. 
%as everyone has to trust the entity responsible for performing the counting.
%Sonja says: I commented this out as it doesn't apply to all. Sometimes you have to trust the data but can count yourself (pictures) or can even take pictures yourself but that's not really verifiability either.

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace or we have to be able to verify their claims.
In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claim should be verifiable).
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants'
privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant in our scheme can be associated with their identity and that their actions are also unlinkable.
%Sonja says: what actions do we refer to here?

%Seb: to do complete the contributions
\emph{Contributions.} In this paper, our main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
Additionally, this verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.

In contrast to the traditional assumption of honest (or at most honest-but-curious) verifiers in distance-bounding algorithms, we propose a way to turn the Schnorr protocol into a distance-bounding protocol resistant against a malicious verifier\footnote{The particular adversary we have in mind here, a verifier impersonating a prover, is actually implicitly covered in public-key distance-bounding protocols such as ProProx~\cite{ProProx}, even though they do not explicitly consider malicious verifiers.}.
%Seb: above, we should put the reference to the Schnorr protocol 
In addition, this allows us to form distance-bounding anonymous credentials.

\emph{Limitations and assumptions.} Some of the assumptions that are required for implementing our proposition are not yet realized (see \cref{assumptions} for more detailed descriptions). 
In particular, not all (or even many) protesters, especially in countries with oppressive regimes, currently possess smartphones.
In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials. 
%Seb: maybe to prevent the above issue, we could require the individual to generate his secret key and only use the authority to obtain a certification on his public key (in the spirit of blind signature)
In this case, it does not make sense to verify any pro-government protests in which Grace's authoritarian regime wants to organize a pro-regime protest to demonstrate its wide support~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Finally, achieving distance-bounding protocols on smartphones is currently not feasible within a meaningful range of distance needed for our scenario.

@@

%Seb: to do, update the outline
\emph{Outline.} The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss how is relationship with electronic voting in \cref{SystemModel}.  
We then present the desired security properties for such a system and subsequently discuss related work in terms of these properties. 
We give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier. \PRIVO, the protocol constructed from the building blocks, is presented next and we analyze its security and privacy as well as performance and implementation issues. We conclude with a discussion.

>>>>

Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in details in \cref{RelatedWork}).
However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
In addition, they also lack verifiability.

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace or we have to be able to verify their claims.
In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claim should be verifiable).
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants'
privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant in our scheme can be associated with their identity and that their actions are also unlinkable.
\sonja{what actions do we refer to here?}

\seb{to do complete the contributions}
\emph{Contributions.} In this paper, our main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
Additionally, this verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.

In contrast to the traditional assumption of honest (or at most honest-but-curious) verifiers in distance-bounding algorithms, we propose a way to turn the Schnorr protocol into a distance-bounding protocol resistant against a malicious verifier\footnote{The particular adversary we have in mind here, a verifier impersonating a prover, is actually implicitly covered in public-key distance-bounding protocols such as ProProx~\cite{ProProx}, even though they do not explicitly consider malicious verifiers.}.
\seb{above, we should put the reference to the Schnorr protocol}
In addition, this allows us to form distance-bounding anonymous credentials.

\emph{Limitations and assumptions.} Some of the assumptions that are required for implementing our proposition are not yet realized (see \cref{assumptions} for more detailed descriptions). 
In particular, not all (or even many) protesters, especially in countries with oppressive regimes, currently possess smartphones.
In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials. 
\seb{maybe to prevent the above issue, we could require the individual to generate his secret key and only use the authority to obtain a certification on his public key (in the spirit of blind signature)}
In this case, it does not make sense to verify any pro-government protests in which Grace's authoritarian regime wants to organize a pro-regime protest to demonstrate its wide support~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Finally, achieving distance-bounding protocols on smartphones is currently not feasible within a meaningful range of distance needed for our scenario.

@@

\seb{to do, update the outline}
\emph{Outline.} The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss how is relationship with electronic voting in \cref{SystemModel}.  
We then present the desired security properties for such a system and subsequently discuss related work in terms of these properties. 
We give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier. \PRIVO, the protocol constructed from the building blocks, is presented next and we analyze its security and privacy as well as performance and implementation issues. We conclude with a discussion.

### 2018-05-22 paper/properties.tex
Transforms comments in code to visible comments

On our setting, we have three potential adversaries: Alice, Eve and Mallory.
%Seb: I changed the name of Grace to Eve to be consistent with the introduction
Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
In contrast, the aim of Eve, the totalitarian dictator, is to decrease the count but also additionally to deanonymize some of the participants in order to arrest them or convince them to change their minds.
Finally, Mallory represents another nation state and has some interest in affecting the stability of Eve's regime, for Mallory's own 
gain, thus supporting either Eve or Alice as he see fits.
Thus, the objective of Mallory will also be to either increase or decrease the count.
%Seb: we have to justify why Mallory is not captured either by Alice or Eve
In addition, Mallory could also have simply for objective to cause a denial-of-service attack on the architecture of \PRIVO.
In the following two subsections, we will now formally define some security properties specifying the computational effort needed by the adversaries to succeed.

@@

%Seb: to complete
\subsubsection{Temporal eligibility}

@@

In addition to the verification requirements, we also need to formalize the privacy properties.
As we indirectly pointed out earlier, we focus on the privacy provided to Alice and the protesters.
In particular our objective is that as long as Alice can conceal her identity at the demonstration and escape without arrest, her support is recorded in the data without her privacy being violated.
%Seb: I think this sentence should be clarified
(Following this line of thinking, it can actually be beneficial for the privacy of the protesters to mix with the participants of any counter-protests --- since the counts will still be correct.)

@@

We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do. 
%Seb: suggestion maybe we should put the following part in the discussion
However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
Thus we need at least participation-proof privacy but receipt freeness is also desired.
In essence, this means that upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
%Sonja says: I'm confused: can we or can we not provide this?
%Seb: I agree with Sonja, it is not clear whether we achieve it or not

>>>>

On our setting, we have three potential adversaries: Alice, Eve and Mallory.
\seb{I changed the name of Grace to Eve to be consistent with the introduction}
Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
In contrast, the aim of Eve, the totalitarian dictator, is to decrease the count but also additionally to deanonymize some of the participants in order to arrest them or convince them to change their minds.
Finally, Mallory represents another nation state and has some interest in affecting the stability of Eve's regime, for Mallory's own 
gain, thus supporting either Eve or Alice as he see fits.
Thus, the objective of Mallory will also be to either increase or decrease the count.
\seb{we have to justify why Mallory is not captured either by Alice or Eve}
In addition, Mallory could also have simply for objective to cause a denial-of-service attack on the architecture of \PRIVO.
In the following two subsections, we will now formally define some security properties specifying the computational effort needed by the adversaries to succeed.

@@

\seb{to complete}
\subsubsection{Temporal eligibility}

@@

In addition to the verification requirements, we also need to formalize the privacy properties.
As we indirectly pointed out earlier, we focus on the privacy provided to Alice and the protesters.
In particular our objective is that as long as Alice can conceal her identity at the demonstration and escape without arrest, her support is recorded in the data without her privacy being violated.
\seb{I think this sentence should be clarified}
(Following this line of thinking, it can actually be beneficial for the privacy of the protesters to mix with the participants of any counter-protests --- since the counts will still be correct.)

@@

We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do.
\seb{suggestion maybe we should put the following part in the discussion}
However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
Thus we need at least participation-proof privacy but receipt freeness is also desired.
In essence, this means that upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
\sonja{I'm confused: can we or can we not provide this?}
\seb{I agree with Sonja, it is not clear whether we achieve it or not}
